\begin{thebibliography}{9}

\bibitem{xu2019anatomy}
J.~Xu y B.~Livshits,
\textit{The Anatomy of a Cryptocurrency Pump-and-Dump Scheme},
en \textit{Proc. 28th USENIX Security Symposium},
pp.~1609--1625, 2019.

\bibitem{kamps2018}
J.~Kamps y B.~Kleinberg,
\textit{To the Moon: Defining and Detecting Cryptocurrency Pump-and-Dumps},
\textit{Crime Science}, vol.~7, no.~18, 2018.

\bibitem{hamrick2018}
J.~T.~Hamrick \textit{et al.},
\textit{An Examination of the Cryptocurrency Pump-and-Dump Ecosystem},
\textit{Information Processing \& Management}, vol.~58, no.~4, 2021.

\bibitem{lamorgia2020}
M.~La~Morgia, A.~Mei, F.~Sassi y J.~Stefa,
\textit{Pump and Dumps in the Bitcoin Era: Real Time Detection of
Cryptocurrency Market Manipulations},
en \textit{Proc. 29th IEEE ICCCN}, pp.~1--9, 2020.
Dataset disponible en: \url{https://github.com/SystemsLab-Sapienza/pump-and-dump-dataset}

\bibitem{lamorgia2023}
M.~La~Morgia, A.~Mei, F.~Sassi y J.~Stefa,
\textit{The Doge of Wall Street: Analysis and Detection of Pump and Dump
Cryptocurrency Manipulations},
\textit{ACM Transactions on Internet Technology}, vol.~23, no.~1, art.~11, 2023.

\bibitem{anderson1958absence}
P.~W.~Anderson,
\textit{Absence of Diffusion in Certain Random Lattices},
\textit{Physical Review}, vol.~109, no.~5, pp.~1492--1505, 1958.

\bibitem{plerou1999}
V.~Plerou \textit{et al.},
\textit{Universal and Nonuniversal Properties of Cross Correlations in
Financial Time Series},
\textit{Physical Review Letters}, vol.~83, no.~7, pp.~1471--1474, 1999.

\bibitem{mantegna1999}
R.~N.~Mantegna,
\textit{Hierarchical Structure in Financial Markets},
\textit{The European Physical Journal B}, vol.~11, no.~1, pp.~193--197, 1999.

\bibitem{nobi2013}
A.~Nobi \textit{et al.},
\textit{Random Matrix Theory and Cross-correlations in Global Financial Indices
and Local Stock Market Indices},
\textit{Journal of the Korean Physical Society}, vol.~62, no.~4,
pp.~569--574, 2013.

\bibitem{newman2003}
M.~E.~J.~Newman,
\textit{The Structure and Function of Complex Networks},
\textit{SIAM Review}, vol.~45, no.~2, pp.~167--256, 2003.

\bibitem{tumminello2005}
M.~Tumminello, T.~Aste, T.~Di~Matteo y R.~N.~Mantegna,
\textit{A Tool for Filtering Information in Complex Systems},
\textit{Proceedings of the National Academy of Sciences}, vol.~102, no.~30,
pp.~10421--10426, 2005.

\bibitem{wang2022}
Q.~Wang \textit{et al.},
\textit{Cyclic Arbitrage in Decentralized Exchanges},
en \textit{Companion Proc. Web Conference 2022}, pp.~12--19, 2022.

\bibitem{soramaki2007}
K.~Soram\"{a}ki \textit{et al.},
\textit{The Topology of Interbank Payment Flows},
\textit{Physica A}, vol.~379, no.~1, pp.~317--333, 2007.

\end{thebibliography}
